Urbanization and Public Transportation of Los Angeles

### 2023-11-08 Paper.Rmd
16 axis -> 14 axis

```{r trend-usage, fig.cap="Line plot of public transportation ridership over time with regression lines"}
# Create the line plot with observed data
p <- ggplot(ridership_trend_long, aes(x=Year, y=TotalRidership, color=Type, group=Type)) +
  geom_line() +
  # Assuming ridership_data has a 'Year' column and the predicted values only.
  # Add the regression lines for predicted bus data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedBusROC, group=1), color="blue", linetype="dashed", size=1) +
  # Add the regression lines for predicted rail data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedRailROC, group=1), color="red", linetype="dashed", size=1) +
  geom_line(data=ridership_data, aes(x=Year, y=PredictedBusROC_poly, group=2), color="hotpink", linetype="dotted", size=2) +
  # Add the regression lines for predicted rail data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedRailROC_poly, group=2), color="darkorange", linetype="dotted", size=2) +
  scale_y_continuous(labels = scales::label_comma(), breaks = scales::pretty_breaks(n = 16)) +
  labs(title="Trend in Public Transportation Usage",
       x="Year",
       y="Total Monthly Ridership",
       color="Transportation Type") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(2019, 2023))

>>>>

```{r trend-usage, fig.cap="Line plot of public transportation ridership over time with regression lines"}
# Create the line plot with observed data
p <- ggplot(ridership_trend_long, aes(x=Year, y=TotalRidership, color=Type, group=Type)) +
  geom_line() +
  # Assuming ridership_data has a 'Year' column and the predicted values only.
  # Add the regression lines for predicted bus data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedBusROC, group=1), color="blue", linetype="dashed", size=1) +
  # Add the regression lines for predicted rail data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedRailROC, group=1), color="red", linetype="dashed", size=1) +
  geom_line(data=ridership_data, aes(x=Year, y=PredictedBusROC_poly, group=2), color="hotpink", linetype="dotted", size=2) +
  # Add the regression lines for predicted rail data (explicit aesthetics)
  geom_line(data=ridership_data, aes(x=Year, y=PredictedRailROC_poly, group=2), color="darkorange", linetype="dotted", size=2) +
  scale_y_continuous(labels = scales::label_comma(), breaks = scales::pretty_breaks(n = 14)) +
  labs(title="Trend in Public Transportation Usage",
       x="Year",
       y="Total Monthly Ridership",
       color="Transportation Type") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(2019, 2023))
